### 2020-10-12 Analysis/Code/Paper.Rmd
updated the bibliography style

---
 title: |
   | Reaching for The Stars: Discounts and Review Tier 
   | Transitions in the Video Games Market

@@

@@

My structural model provides further insight into the relative contributions of the variance and the selection effects to the observed behavior. I estimate the effect of discounts on the probabilities to leave positive and negative reviews. I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion. Thus, I attribute firms' behavior to the variance effect. While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions. I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition. I find that, in the absence of the selection effect, products that are close to a review downgrade are significantly less likely to discount, which is consistent with the idea that the variance effect is negative for such products. I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.

@@

# Conclusion
\label{conclusion}

>>>>

---
 title: |
   | Reaching for The Stars: Discounts and Review Tier 
   | Transitions in the Video Games Market
   | \href{https://github.com/dmsorokin/PaperRepository/blob/gh-pages/Sorokin_JMP_2020.pdf}{\large Click for the Latest Version}

@@

 abstract: |
  \\singlespacing I document that firms in online marketplaces use price promotions 
  to facilitate transitions to better review tiers (similar to the number of stars on
  Amazon.com). I find that firms close to going one tier up are 4-9% more 
  likely to discount. I theorize that two effects could be at play. The selection effect 
  arises because customers who buy during a discount could be different from the regular 
  ones, and could potentially leave more positive reviews. The variance effect reflects 
  the idea that positive reviews could help the firm move up a review tier, while 
  negative reviews would keep the tier unchanged, minimizing the downside risk 
  of giving a discount. To test my hypotheses, I estimate a simple structural 
  model of demand and reviewing behavior, and develop a new approach to estimating demand 
  from data on product usage. I do not find evidence that the selection effect is 
  positive. I find evidence of the importance of the variance effect: when 
  the selection effect is zero, firms close to downgrading their review tier are 6% 
  less likely to give a discount, consistent with preferring less variance. I also 
  find that consumers are significantly more likely to leave a review when purchasing 
  during a discount. Additional findings include estimates of the causal effect of 
  reviews on sales and equilibrium discount elasticities in an important market 
  not previously studied.

@@

My structural model provides further insight into the relative contributions of the variance and the selection effects to the observed behavior. I estimate the effect of discounts on the probabilities to leave positive and negative reviews. I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion. Thus, I attribute firms' behavior to the variance effect. While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions. I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition. I find that, in the absence of the selection effect, products that are close to a review downgrade are 6% less likely to discount, which is consistent with the idea that the variance effect is negative for such products. I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.

@@

# Conclusion
